Development of Performance Regression Analysis Tool using Distributed Tracing on Microservice-based Application\\

### 2022-06-23 paper.tex
txs auto checkin

Given the distributed nature of Microservices, it will be difficult for developers if regression detection is carried out with an individual approach on each existing servce especially when the number of existing servce is very large, and the interdependence relationship between services becomes complicated. Therefore, to overcome performance regression in Microservice-based application, an approach that does not require developers to source search is needed
problem on each service individually. So that in the case of detection and regression analysis of Microservice-based application performance, the first approach is more suitable
to use.

>>>>

Given the distributed nature of Microservices, it will be difficult for developers if regression detection is carried out with an individual approach on each existing servce especially when the number of existing servce is very large, and the interdependence relationship between services becomes complicated. Therefore, to overcome performance regression in Microservice-based application, an approach that does not require developers to source search is needed. So that in the case of detection and regression analysis of Microservice-based application performance, the first approach is more suitable to use.
